A Component-Based Sensor Network for \\ Environmental Monitoring

### 2009-03-12 docs/icccn2009/paper.tex
Adding
git-svn-id: svn://localhost/netbeams/trunk@369 559edde2-a4d4-44e0-96fc-4035e40d7396

After the DSP server receives the message, it directly delivers to the
local DSP Broker all the messages contained in the Messages Container server.
In addition to that, the Messages Container might also include an attribute
called acknowledgeUntil, which determines the next actions that will occur in
the system.

>>>>

After the DSP Wire Transport Server receives the Messages Container (3), it
unmarshalls the messages and forward them to the local DSP Broker.

The reception of those messages will ALWAYS depend on the local DSP Broker and
its combination with the Matcher. The steps (4), (5) and (6) are the
actual reception of DSP messages. Container might also include an attribute
called acknowledgeUntil, which determines the next actions that will occur in the system.
